MFCCs, Chroma Features, and Spectrogram Images for Deepfake Audio Classification Using Machine Learning

### 2024-12-06 paper/ieeepaper.tex
added paragraph about cnns

\subsection{Convolutional Neural Networks}
Nora TODO
\subsubsection{VGG16}
Nora TODO
\subsubsection{ResNet50}
Nora TODO

@@

\vspace{12pt}
\color{red}
delete me

>>>>

\subsection{Convolutional Neural Networks}
A Convolutional Neural Network, or CNN, is a type of deep learning model specifically designed to process data with a grid-like topology, such as images. It accepts an image with H rows and W columns, and three channels (R, G, B color channels) as input. The input then goes through several layers. First, the Rectified Linear Unit, or ReLU, is a transformation layer. It performs a truncation for each individual element in the input. Next, the input is fed to the convolution layer. This layer searches for edges in the image, and outputs a matrix with these features highlighted. Finally, the pooling layer will reduce the matrix while retaining important features. Then, the process repeats until a classification can be made about the inputted image \cite{wu2017introduction}.

\subsubsection{VGG16}
Nora TODO
\subsubsection{ResNet50}
Nora TODO

@@
